%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \centerline{\textbf{{\LARGE Yihung Yu}}}\vspace{+5pt} \\
  \centerline{~~~~~~~Mobile~~~~~~~$||$~~~~~~~~~~~~~Email~~~~~~~~~~~~~$||$~~~~~~~~~~~GitHub~~~~~~~~~~} \\
  \vspace{+5pt}\centerline{+886 921605518~$||$~\href{henry840227@gmail.com}{henry840227@gmail.com}~$||$~\href{https://github.com/henrydsg}{github.com/henrydsg} } \\
  \textbf{Interest:~Autonomous Vehicle, Large-scale Distributed system} \\
  \textbf{Objective:~R\&D position in the field of localization, planning, computer vision} \\
  \textbf{Sponsorship or fully remote work required}
\end{tabular*}

\vspace{-2pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~C++, Python, Matlab}
  \resumeSubItem{Tools \& Libs}{~Docker, Git, CMake, GDB, Eigen, Ceres-solver}
	\resumeSubItem{Platforms}{~~~~~~Linux, Android}
  \resumeSubItem{Frameworks}{~~~ROS}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{\href{https://www.gallopwave.com/}{Gallopwave Co.}}{Taipei, Taiwan}
      {Senior R\&D Engineer}{Nov 2020 - Feb 2022}
    \resumeItemListStart
        \resumeItem{Inverse-depth Parameterization of Image Feature for Visual Inertial Odometry}
          {Designed and Implemented inverse-depth parametrization of image features and a easy-to-switch structure to rapidly test the performance of different types of parametrization. }
        \resumeItem{SLAM Data Read/Write System}
          {Re-defined and Re-implemented a sensor data read/write library in C++ which is extremely fast for data seeking and traversing.}
        \resumeItem{Playback Visualization Tool}
          {Designed and implemented a 3D, viewpoint-adjustable, fast, high-quality visualization tool for debugging in Unity framework.}
        \resumeItem{Protection Level Estimation for Global Localization System on Commercial-level Sedan}
          {Designed and implemented a light-weight protection level estimation algorithm performing high integrity and fair availability.}
        \resumeItem{Cross-platform Porting}
          {Modified existing CMake pipeline to make the cross-compiling process of the VIO system a one-click procedure.}
        \resumeItem{CI/CD Pipeline}
          {Co-implement the CI/CD pipeline of the VIO system which can effectively detect any significant regression of the performance.}
      \resumeItemListEnd
    \resumeSubheading{\href{http://www.kingwaytek.com/}{Kingwaytek Technology}}{Taipei, Taiwan}
      {R\&D Engineer}{Nov 2019 - Oct 2020}
		\resumeItemListStart
        \resumeItem{LiDAR Localization}
          {Redesigned the pipeline of Autoware's NDT localizer to realize fully automated localization in several controlled environment with point cloud map.}
        \resumeItem{MPC Waypoint Follower}
          {Refactored and tuned Autoware's MPC waypoint follower to run smoothly on a e-bus in several contorlled area.}
        \resumeItem{Steering Angle Calibration}
          {Designed and executed a low-cost (less than 200 USD, no additional cost for repeating the experiment) experiment to acquire steering wheel - steering angle curve.}
		\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, Berkeley}{California, Berkeley}
{Master of Engineering - Mechanical Engineering}{Aug 2018 - May 2019}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Selected Courses:} Intro to AI, Advanced Control System (Model Predictive Control), Linear Control System, Nonlinear Control System}}}
\resumeSubheading
{National Taiwan University}{Taipei, Taiwan}
{Bachlor of Science - Mechanical Engineering}{Sep 2013 - June 2017}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Selected Courses:} Data Structure and Algorithms, Intro to Robotics, Advanced Dynamics}}}
\resumeSubHeadingListEnd

\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {NTU Mechanical Engineering Student Association}{Taipei, Taiwan}
    {Led and organized student session events and arranged activities of the department.}{June 2015 - June 2016}
\vspace{5pt}
\resumeSubHeadingListEnd

\end{document}
